---
title: "Group 1"
author: "Hannah Lee"
date: '2022-11-22'
output: html_document
---

```{r}
library(tidyverse)
library(plotly)
library(broom)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(modelr))
install.packages("ggpubr")
library("ggpubr")
score <- read.csv("exams.csv")
```
# wrangling

```{r}
exam_df <-
  score %>%
  mutate(eng.score = (reading.score + writing.score)/2) %>%
  select(c(6, 9))
```
# summerize
```{r}
exam_df %>%
  summarize(
     eng_mean = mean(eng.score),
     eng_median = median(eng.score),
     eng_standard_deviation = sd(eng.score),
     eng_minimum = min(eng.score),
     eng_maximum = max(eng.score)
  )
```




# lm


```{r}
exam_model <- lm( math.score ~ eng.score, exam_df)
```

```{r}
exam_model %>%
tidy()
```

```{r}
exam_model %>%
  glance() %>%
  select(1:3)
```

```{r}
exam_new <- exam_df %>%
  add_predictions(exam_model) %>%
  add_residuals(exam_model)
```



```{r}
ggplot(exam_df) +
  geom_point(mapping = aes(x = eng.score, y = math.score)) +
  geom_abline(slope = exam_model$coefficients[2],
              intercept = exam_model$coefficients[1]	) +
   labs(
  title = "Relationships with math score and english score",
  y = "math score", x = "english score"
)
```
# 3 assumptions


1. lineraity: When looking at the plot drawn above, the line of best fit seems to well explain the distribution of the points. Thus, we can say that the relationship is linear/

2. constant variability: when covering the outliers, the distribution of points( how far away from the line of best fit) is pretty constant. 

3. nearly normal residuals: Looking at the graph above, the histogram is bell shaped. Thus, the residuals can be considered nearly normal residual.
```{r}
exam_new %>%
  ggplot() +
  geom_histogram(mapping = aes(x = resid), color = "darkblue", fill = "lightblue",  binwidth = 3.9) +
   labs(
  title = "Examination of the risiduals of exam_df",
  y = "count", x = "residual")

```


# interpretation

The Linear Models can be used to measure the relationship between variables, or to make  predictions.
When since the lm meets all 3 assumptions, we can say that the english score (average of reading and writing score) might effect the math score.

The two variables might not explain the causation, but we can say that there is a linear correlation, and the relationship is linear. It is a positive relationship, so we can predict that students with high english scores will probably have a high math score. 


